---
title: "Two Dimensional Data Worksheet"
output: html_document
---

# Two Dimensional Data Worksheet

This worksheet focuses on manipulating two dimensional data using Python and Pandas.

```{r message=FALSE, warning=FALSE, echo=FALSE}
# install.packages("devtools")
# devtools::install_github("hadley/tidyverse")
library(tidyverse)
```

Create a dataframe called `twitter` from the CSV file

_Note if this is breaking your machine there is a smaller data set in the data file called twitter1-small.csv_

```{r}

```


## Exercise 1

Using the twitter data frame, count the appearances of each `Username`, get the top 10 active users and output the sorted result.

1. Start with `dplyr::count` on `Username`
2. Grab the top 10 with `dplyr_top_n`
3. sort with `dplyr::arrange`, can make it descending by wrapping the sort variable with `desc()`

```{r}

```

## Exercise 2
Using the original twitter data set, create a second DataFrame called `twitterSummary` which contains the following columns:

* Username
* Friends 
* Followers

Next add a column called `ffratio` which contains the ratio of friends to followers.  Show the first few lines.

```{r}

```

## Exercise 3

In the `data` folder, there is file called `studentData.csv` consisting of students and test scores.  Write a script which calculates each students' average test score and adds that as a column to the DataFrame.  

The first person to tell me which student has the highest average test score, and what it is wins something.

```{r}

```

## Exercise 4
Using the twitter data, find all the users with Facebook accounts and create a new column called `FacebookID` which contains the users' Facebook ID.  As you can see in the URL below, a user's Facebook ID can be found in the URL column, http://www.facebook.com/profile.php?id=5141860.  Extract this the ID. Don't forget to remove all the invalid or empty IDs.  

1. Use the Function supplied to extract "?id=<numbers>" from the URL
    + Note the function does not filter for facebook, so you will have to prefilter the data for facebook, try using `dplyr::filter` with `grepl` inside the function.
2. Once complete, filter out the data where the FacebookID is not NA (`!is.na()`).

_Note: there are a lot of [ways to pull a substring from a string](http://stackoverflow.com/questions/2192316/extract-a-regular-expression-match-in-r-version-2-10):_

```{r}
library(stringr) # do you have this installed?
getfacebook <- function(x) {
    # this pivots on grepl (logical grep returns TRUE or FALSE)
    # if it contains facebook, then split on ?id=, grabbing the remaining text
    # else return NA
    ifelse(grepl('\\?id=\\d+', x), 
           str_extract(str_extract(x, "\\?id=\\d+"), "\\d+"),
           NA)
}

```