---
title: "Visualization Worksheet"
output: html_document
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
```

# Data Visualization Worksheet
This worksheet will walk you through the basic process of preparing a visualization using R/ggplot2.  

For this exercise, we will be creating a line plot comparing the number of hosts infected by the Bedep and ConfickerAB Bot Families in the Government/Politic sector.

## Prepare the data
The data we will be using is in the `dailybots.csv` file which can be found in the `data` folder.  As is common, we will have to do some data wrangling to get it into a format which we can use to visualize this data.  To do that, we'll need to:
1.  Read in the data
2.  Filter the data by industry and botnet

###  Step 1 Read in the data

```{r}
bots <- read_csv('../../data/dailybots.csv')

```

### Step 2: Filter the Data
The next step is to filter both by industry and by botfam. Filter for "Government/Politics" in the industry, and then bot family should be either ConfickerAB or Bedep.


```{r}
toplot <- ...
  filter(industry == "Government/Politics",
         botfam %in% c('ConfickerAB', 'Bedep'))
  
ggplot(toplot, aes(date, hosts, color=botfam)) + geom_line()
```

### pretty it up (1)

* Apply `theme_bw()` to the plot,
* Move the legend to the bottom (look at ?theme for 'legend_position')

```{r}
ggplot(toplot, aes(date, hosts, color=botfam)) + geom_line() +
  theme_bw() +
  theme(legend.position="bottom")
```

### make it bigger

you won't see any difference unless you "Knit" the document, but the image size 
can be set in the {r} tag.

```{r fig.width=4, fig.height=3}
ggplot(toplot, aes(date, hosts, color=botfam)) + geom_line() +
  theme_bw() +
  theme(legend.position="bottom")
```

### Interactive

We won't go to interactive graphics quite yet, but if you wanted to look for an interactive option, see
[HTML Widgets](http://www.htmlwidgets.org/showcase_dygraphs.html).
http://rstudio.github.io/dygraphs