---
title: "Supervised Worksheet"
output: html_document
---

Load up Libraries...

```{r}
library(tidyverse)
library(caret)
```

Load up the data, be sure to set the target variable as a factor (For R)

```{r}
dga <- read_csv("data/dga-full.csv") %>%
  mutate(dsrc = factor(dsrc))
# helps to have the target class as a factor
```

### Split data into a training and testing data set

Take a look at the help for `createDataPartition` in the `caret` package.

### Just extract the data for "alexa" and "nivdort"

You will be creating a two-class classifier.

```{r}

```

### Train both a Random Forest and Support Vector Machine on these

Traing the first model using Random Forest, and the second for a Support Vector Machine.

You will compare the two and see which performs better on the data.

```{r}
# . . .

print(rfFit)

# . . .
print(svmFit)
```

### Look at the confusion matrix on the Random Forst model using the test data 

```{r}
```

### Look at the confusion matrix on the Random Forst model using the test data 

```{r}
```

Which one looks better?

### Look at the variable importance in the Random Forest Model

```{r}
```
